---
title: "Homework 5"
author: "Anna Ostropolets"
date: "11/12/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(RCurl)
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1

```{r data}
# loading the data
url <- getURL("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")
data <- read.csv(text = url)

```

## describiing the raw data

The data contains `r nrow(data)` observations of homicides, committed in `r data %>% distinct (city) %>% count()` cities in `r data %>% distinct (state) %>% count()` states.
It has the names of the victims, their age as well as their gender and the disposition of cases and location (latitute and longitude).

```{r summary, warning=FALSE, message=FALSE}
# summarizing numebr of  homicides
aggregated_data<-
  data %>%
  mutate(
    city_state = str_c(city, state, sep = ","),
    status = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved",
    ),
    victim_age = na_if(victim_age,'Unknown')
  ) %>%
  filter(city_state != "Tulsa_AL") %>%
  group_by(city_state) %>%
  summarize (total_cnt = n(),
             unsolved_cnt = sum(status == "unsolved")) 
```


## create a prop.test function to estimate proportion of homicides and use it for all cities avaliable

```{r prop_test, message=FALSE, warning=FALSE, error=FALSE}

prop.test(
  aggregated_data %>% filter(city_state == "Baltimore,MD") %>% pull(unsolved_cnt), 
  aggregated_data %>% filter(city_state == "Baltimore,MD") %>% pull(total_cnt)) %>% 
  broom::tidy()
  
results_df <- 
  aggregated_data%>%
  mutate(
    prop_tests = map2(.x = unsolved_cnt, .y = total_cnt, ~prop.test(x=.x, n= .y)), tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>%
  select(-prop_tests) %>%
  unnest(tidy_tests) %>%
  select(city_state, estimate, conf.low, conf.high)

```

## plot estimates and CIs

```{r plot}
results_df %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


# Problem 2
## creating dataframe with tidy data for study participants


```{r study_data, message = FALSE}
study_data <- 
  tibble(
    path = list.files("./data")) %>% 
  mutate(path = str_c("./data/", path),
         data = map(.x = path, ~read_csv(.x))) %>% 
  unnest(data) %>% 
  mutate(id = str_extract(path, "\\d+"),
         subject_id = as.numeric(id),
         arm = str_extract(path, "con|exp")) %>% 
  relocate(id, arm, path,everything()) %>% 
  mutate(arm = recode(arm, con = "control", exp = "experimental")) %>% 
  pivot_longer(week_1:week_8,
               names_to = "week",
               names_prefix = "week_",
               values_to = "value") %>%
  select (subject_id, arm, week, value)
```

## Creating a spaghetti plot with observations on each subject over time.

```{r spaghetti_plot}
study_data %>% 
  ggplot(aes(x = week, y = value, group = subject_id, color = arm)) +
  geom_path()
```

On average, subjects in experimental group have higher values than in the control group. There is also an increase in values over time in experimental group while in the control group there are no significant changes.


# Problem 3

```{r sim}

# Generate 5000 datasets with n = 30, mu = 0, and sigma = 5 and extract their means and p-values:

set.seed(3)

sim_ft <- function(n = 30, mu, sigma = 5) {
  
  sim_data = tibble(
    x = rnorm(n = n, mean = mu, sd = sigma))
  sim_data %>% 
    summarize(mu_hat = mean(x),
              p_value = t.test(x) %>% 
  broom::tidy() %>% pull(p.value))
}

sim_results <-
  rerun(5000, sim_ft(mu = 0)) %>% 
  bind_rows()
```

```{r mu_16}
# Repeat the above for μ={1,2,3,4,5,6}

sim_results_2 <- 
  tibble(new_mu = c(0:6)) %>% 
  mutate(
    output = map(.x = new_mu, ~rerun(5000, sim_ft(mu = .x))),
    estimate = map(output, bind_rows)) %>% 
  select(-output) %>% 
  unnest(estimate)

```

```{r plots}
# A plot showing the proportion of times the null was rejected vs the true value of μ
sim_results_2 %>% 
group_by(new_mu) %>%
  summarize(
    total = n(),
    rejected = sum(as.numeric(p_value) < 0.05 & mu_hat!=new_mu)) %>% 
  ggplot(aes(x = new_mu, y = rejected/total)) +
  geom_point() +
    labs(title = "Rejection of null hypothesis for mu",
       x = "True mu",
       y = "Proportion of rejected null hypotheses")  
``` 
Increase in estimate is associated with increase in power

```{r plots_2}
# A plot showing the average estimate of μ̂ the true value of μ
sim_results_2 %>% 
group_by(new_mu) %>%
  summarize(avg_estimate = mean(new_mu)) %>% 
  ggplot(aes(x = new_mu, y = avg_estimate)) +
  geom_point() +
    labs(title = "Average estimated mu vs true mu",
       x = "True mu",
       y = "Estimated mu")  

sim_results_2 %>% 
  group_by(new_mu) %>% 
  filter(as.numeric(p_value) < 0.05 & mu_hat!=new_mu) %>% 
  summarize(avg_estimate = mean(new_mu)) %>% 
  ggplot(aes(x = new_mu, y = avg_estimate)) +
  geom_point() +
  geom_point(color = "purple")
# on the x axis. Make a second plot (or overlay on the first) the average estimate of μ̂
# only in samples for which the null was rejected on the y axis and the true value of μ
# on the x axis.

```
